How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-08 tse-paper/content.tex
writing study discussion draft, pbe and cts glue text, build log analysis in industry, subfigure for chunk examples

\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
  \caption{Example of a log chunk explaining why an Android
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example-1}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
  \caption{Another example of a log chunk explaining why an Android
  build failed.}
  \label{lst:chunk-example-2}
\end{figure}

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
StartExtraction(RegexPair("Colon/$\circ$/Line Separator",
"ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
"Line Separator/$\circ$/Line Separator"))
  \end{lstlisting}
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
  \label{lst:prose-program-simplified}
\end{figure}

@@

The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

\begin{table*}[]
\centering
\caption{Overview of buildlog analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Source(s)	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression  &
\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2019study,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language \\ Processing}  &
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}

@@

25\% of the articles claimed their implementation is available, however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
\emph{Maven Log Analyzer}, % TODO: cite
another two the \emph{MAKAO} tool.
% TODO: cite

\subsubsection{Build Logs}
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
and 10\% logs produced by Ant.
% TODO: cite
Sometimes this limitation to a specific build tool is motivated by
% TODO: PIT tool, often: much variety in log format only time for
one parser

@@

The main platform that build logs were collected from is Travis
CI, % TODO cite.
which was used in 38\% of cases.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

@@

\subsection{Discussion}
Our literature survey sheds light on how build log analysis is used within
computer science research.
We saw that various researchers process build logs to support their
research, often because the logs provide more or the necessary information
to the researchers.
% TODO cite 'Autmoated localization for unreproducible builds
Automated approaches are necessary as many studies target a large
number of
builds.
Most of the articles which explicitly mention a manual analysis of
the logs
only restrict their work to few logs or take a ``representative sample to
make manual analysis feasible''.
% TODO cite: a study of build inflation in 30 mil CPAN builds

\subsubsection{Retrieved Information}
why from build logs? not avaliable in cleaner format much use for
research, a bit of developer information / tools following: research
so many logs that unfeasible to do manually, less focus on tools for
devs (caveat! we excluded books and documentation on industrial tools
-> many approaches there to make build logs digestible, tough many
focus on general minimizing of the data presented, not retrieving
specific chunks)

\subsubsection{Retrieval Technique}
broadly mentioned shortly, rarely explained in detail we follow that
researchers often see this as an unimportant side fact work needed to
be done to get the big work done

\subsubsection{Build Logs}
often focussed on specific logs, sometimes mentioned because of effort
developing a parser other times also because other tools used in
further research are limiting the scope (reference paper with PIT
tool).
many focus on maven because of it's prevalence also in respect
to other tools much research done on travis ci logs b/c of their
abundance and open availability

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:expl-pbe}
% % \emph{Programming by Example} is a technique which synthesizes
% % programs according to in- and output examples provided by the user.
% % It enables users to create programs without a priori programming
% % knowledge~\cite{mayer2015user}.
% In the context of text extraction
% % through regular expressions, Programming by Example relieves the
% % developer from having to understand the whole document structure to
% % solve a single extraction task~\cite{le2014flashextract:}.
% In this
% % work, we refer to our interpretation of Programming by Example as
% % \emph{PBE}\@.
% We investigate the suitability of PBE to retrieve
% % information chunks from build logs.
% In the following, we explain the
% % configuration and application of PBE to chunk retrieval from CI
% % build logs.

% TODO later: we should make sure to at least mention PROSE
% _somewhere_, it's crucial for why PBE is how it is
\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The
\emph{input} is the text of the build log file.
The \emph{output} is
an array of substrings of the log file text, representing the
substrings that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The
PROSE program synthesis then tries to construct a program consistent
with all training examples.
% % A program is consistent with an example if it returns the defined
% % output when executed on the defined
% % input~\cite{mitchell1982generalization}.
% PBE reports an error back to the user if it could not synthesize a
% consistent program.
% % The program synthesis builds on the FlashExtract DSL, which in turn
% % uses the FlashMeta algorithm.
% Both are described in
% % Section~\ref{sec:rw-prose}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.

% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
% % Text Similarity approaches are used to filter unstructured textual
% % software
% %
%artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
% % One common and simple technique is the Vector Space Model.
% We
% % investigate when text similarity is a suitable technique to retrieve
% % information chunks from build logs.
% In the following we will explain
% % the concept of how we apply text similarity to information retrieval
% % from CI build logs, which we refer to as \emph{CTS}\@.

@@

% TODO cite http://text2vec.org/
Our implementation of CTS is dependent on the library {\tt text2vec}
and the way it splits strings into word tokens.
On the other hand,
{\tt text2vec} is the de-facto standard library to do word embeddings
in R.
We intentionally chose a simple, minimally configured and tuned
approach to compare against.
Tuning the text similarity
meta-parameters more to the specific use case of chunk retrieval from
build logs would yield better chunk retrieval results.

@@

\section{Future Work}
% TODO: survey build logs tools in industry

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
  the comparative
  study in this paper, though it can be the basis for various further
  analyses of build log data.
The keywords, for example, can be
  investigated to answer which keywords are used to search for the
  reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and
  tested each chunk retrieval technique on examples from the same
  repository.
We propose to analyze how techniques could be trained
  across repositories, building the cornerstones for build
  environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
  paper investigates the three chunk retrieval techniques PBE, CTS and
  KWS\@.
Our study design can be reused to evaluate other build log
  analysis techniques, such as the diff and information retrieval
  approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We
  investigated basic configurations of existing techniques applied to
  chunk retrieval from build logs.
In a next step, each of these
  techniques could be refined to better approach the domain of build
  logs.
The \emph{LogChunks} data set and our study results act as a
  baseline to benchmark such technique improvements.
We propose the
  following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program
      synthesis through PROSE ranks possible programs according to
      what the user most likely intended.
One could adapt the ranking
      rules provided by the FlashExtract DSL to fit common build log
      chunk retrieval tasks.
FlashExtract includes special tokens when
      enumerating possible regular expressions.
One could extend these
      with tokens found in build logs, such as ``-'',``='',``ERROR''
      or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information
      retrieval techniques have various meta-parameters which can be
      optimized for the specific use
      case~\cite{panichella2016parameterizing}.
We propose to further
      investigate improvements in preprocessing of the log text, in
      tokenization of the log lines into terms and in stop words
      lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
  analysis of the output produced by the chunk retrieval focuses on
  precision and recall.
We propose to investigate how useful these
  outputs are to developers through controlled experiments.
\end{itemize}

>>>>

\begin{figure*}[!t]
  \centering
\begin{subfigure}[t]{\columnwidth}
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
FAILURE: Build failed with an exception.

@@

* Try:
  \end{lstlisting}
\end{subfigure}
  \caption{Two examples of log chunks explaining why an Android
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example}
\end{figure*}

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
StartExtraction(RegexPair("Colon/$\circ$/Line Separator",
"ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
"Line Separator/$\circ$/Line Separator"))
  \end{lstlisting}
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example}}
  \label{lst:prose-program-simplified}
\end{figure}

@@

The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example} shows two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

\begin{table*}[]
\centering
\caption{Overview of buildlog analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Source(s)	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression  &
\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language \\ Processing}  &
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}

@@

25\% of the articles claimed their implementation is available, however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

\subsubsection{Build Logs}
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by
Gradle~\cite{gradle2020website}
and 10\% logs produced by Ant~\cite{ant2020website}.

Sometimes this limitation to a specific build tool is motivated by
aspects separate from the build log analysis.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within our survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

The main platform that build logs were collected from is Travis
CI~\cite{travisci2019webpage},
which was used in 38\% of cases.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

@@

\subsection{Discussion}
Our literature survey sheds light on how build log analysis is used within
computer science research.
In this section we will summarize our findings and relate them to the
approach we are taking to improve build log analysis with chunk
retrieval techniques.

We saw that various researchers process build logs to support their
research, often because the logs provide more or the necessary information
to the researchers~\cite{ren2018automated}.
Most of the articles which explicitly mention a manual analysis of
the logs only restrict their work to few logs or take a
``representative sample to make manual analysis
feasible''~\cite{zolfagharinia2017not}.
Automated approaches are necessary as many studies target a large
number of builds.
The chunk retrieval techniques we investigate within this article are
automated, apart from their configuration through training examples.

We have observed very little reuse of build log analysis tools.
This can stem from the fact that publishing replication packages and
research prototypes became popular only in recent years or from the
high specialization of the developed tools in regards to supported
build environments and targeted information.
Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
We implement build environment agonostic build log analysis
techniques, which are customized to a specific project by
the training examples which the user provides.
In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
data set we chose for our evaluation covers a broad range of build
environments.
Further, the training examples also specify the log chunk targeted by the
retrieval, which enable our chunk retrieval techniques to retrieve a
broad range of information from build logs.

Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone'', other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.
For this reason, we are focussing % TODO: less development time,
% only giving examples

% \subsubsection{Retrieved Information}
% why from build logs? not avaliable in cleaner format much use for
% research, a bit of developer information / tools following: research
% so many logs that unfeasible to do manually, less focus on tools for
% devs (caveat! we excluded books and documentation on industrial tools
% -> many approaches there to make build logs digestible, tough many
% focus on general minimizing of the data presented, not retrieving
% specific chunks)

% \subsubsection{Retrieval Technique}
% broadly mentioned shortly, rarely explained in detail we follow that
% researchers often see this as an unimportant side fact work needed to
% be done to get the big work done

% \subsubsection{Build Logs}
% often focussed on specific logs, sometimes mentioned because of effort
% developing a parser other times also because other tools used in
% further research are limiting the scope (reference paper with PIT
% tool).
% many focus on maven because of it's prevalence also in respect
% to other tools much research done on travis ci logs b/c of their
% abundance and open availability

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:expl-pbe}
The area of \emph{Programming by Example} aims to capture the
intent of the user through examples which they provide.
Leveraging this apprach, we implemented a chunk retrieval technique
for build logs.
Our implementation is based and highly influenced by the
\emph{Microsoft PROSE library}~\cite{prose2019webpage}.
The PROSE library is powered by the generic program synthesis framework
\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
Both enable us to synthesize regular expression programs
consistent~\cite{mitchell1982generalization} with a set of in-
and output examples given by the user.
The usage of example enables the user to configure a chunk
retrieval without understanding the whole structure of
the build log.
% % It enables users to create programs without a priori programming
% % knowledge~\cite{mayer2015user}.
% In the context of text extraction
% % through regular expressions, Programming by Example relieves the
% % developer from having to understand the whole document structure to
% % solve a single extraction task~\cite{le2014flashextract:}.
% In this
% % work, we refer to our interpretation of Programming by Example as
% % \emph{PBE}\@.
% We investigate the suitability of PBE to retrieve
% % information chunks from build logs.
% In the following, we explain the
% % configuration and application of PBE to chunk retrieval from CI
% % build logs.

% TODO later: we should make sure to at least mention PROSE
% _somewhere_, it's crucial for why PBE is how it is
\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
an array of substrings of the log file text, representing the
substrings that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.
% % A program is consistent with an example if it returns the defined
% % output when executed on the defined
% % input~\cite{mitchell1982generalization}.
% PBE reports an error back to the user if it could not synthesize a
% consistent program.
% % The program synthesis builds on the FlashExtract DSL, which in turn
% % uses the FlashMeta algorithm.
% Both are described in
% % Section~\ref{sec:rw-prose}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts
~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
and simple Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.
% Text Similarity approaches are used to filter unstructured textual
% software artifacts.
% One common technique
% %
%artifacts.
% % One common and simple technique is the Vector Space Model.
% We
% % investigate when text similarity is a suitable technique to retrieve
% % information chunks from build logs.
% In the following we will explain
% % the concept of how we apply text similarity to information retrieval
% % from CI build logs, which we refer to as \emph{CTS}\@.

@@

Our implementation of CTS is dependent on the library
{\tt text2vec}~\cite{text2vec2019webpage}
and the way it splits strings into word tokens.
On the other hand,
{\tt text2vec} is the de-facto standard library to do word embeddings
in R.
We intentionally chose a simple, minimally configured and tuned
approach to compare against.
Tuning the text similarity
meta-parameters more to the specific use case of chunk retrieval from
build logs would yield better chunk retrieval results.

@@

\section{Future Work}

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Systematic Survey of Industry Approaches for Build
  Log Analysis} Our survey is limited to academic work and articles.
  However, handling build logs is a challenge for a wide range of
  practitioners as well.
  We propose to investigate the methods used in industry to analyze
  build logs.
  An example is the Jenkins \emph{build-failure-analyzer}
  plugin~\cite{jenkins2020failure-analyzer} or automatically
  inferred test results in Azure~\cite{azure2020inferred}.
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
  the comparative
  study in this paper, though it can be the basis for various further
  analyses of build log data.
  The keywords, for example, can be
  investigated to answer which keywords are used to search for the
  reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and
  tested each chunk retrieval technique on examples from the same
  repository.
  We propose to analyze how techniques could be trained
  across repositories, building the cornerstones for build
  environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
  paper investigates the three chunk retrieval techniques PBE, CTS and
  KWS\@.
  Our study design can be reused to evaluate other build log
  analysis techniques, such as the diff and information retrieval
  approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We
  investigated basic configurations of existing techniques applied to
  chunk retrieval from build logs.
  In a next step, each of these
  techniques could be refined to better approach the domain of build
  logs.
  The \emph{LogChunks} data set and our study results act as a
  baseline to benchmark such technique improvements.
  We propose the
  following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program
      synthesis through PROSE ranks possible programs according to
      what the user most likely intended.
      One could adapt the ranking
      rules provided by the FlashExtract DSL to fit common build log
      chunk retrieval tasks.
      FlashExtract includes special tokens when
      enumerating possible regular expressions.
      One could extend these
      with tokens found in build logs, such as ``-'',``='',``ERROR''
      or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information
      retrieval techniques have various meta-parameters which can be
      optimized for the specific use
      case~\cite{panichella2016parameterizing}.
      We propose to further
      investigate improvements in preprocessing of the log text, in
      tokenization of the log lines into terms and in stop words
      lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
  analysis of the output produced by the chunk retrieval focuses on
  precision and recall.
We propose to investigate how useful these
  outputs are to developers through controlled experiments.
\end{itemize}
